CUNY SPS DATA-607 Week 9 Assignment

### 2018-10-22 DATA607/Week_9_Assignment.Rmd
Modified Week_9_Assignment.Rmd
Linted document and made minor changes

```{r}
library(httr)
# Load my API key into api_key
source('hidden/NYT API.R')
url <- paste0('https://api.nytimes.com/svc/topstories/v2/upshot.json?api-key=', api_key)
response <- GET(url)
```

@@

```{r, message=FALSE}
library(jsonlite)
json <- fromJSON(content(response, as = "text"))
df <- data.frame(json$results)
```

>>>>

```{r}
library(httr)
source("hidden/NYT API.R") # Load my API key into api_key
base_url <- "https://api.nytimes.com/svc/topstories/v2/upshot.json"
url <- paste0(base_url, "?api-key=", api_key)
response <- GET(url)
```

@@

```{r, message=FALSE}
library(jsonlite)
json <- fromJSON(content(response, as = "text"))
df <- data.frame( json$results )
```
